### 2024-09-17 base-rates.qmd
20240917 - copyediting

Example 3B: Now, consider that a second plan just hit the World Trade Center.
What is the probability that a terror attack occurred given that a second plane hit the World Trade Center?

- the revised [prior probability](#sec-baseRate) that terrorists crash a plane into a Manhattan skyscraper (from Example 3A): 38.46272%
- the [conditional probability](#sec-conditionalProbability) that a plane crashes into a Manhattan skyscraper if terrorists are attacking Manhattan skyscrapers: 100%
- the [conditional probability](#sec-conditionalProbability) that a plane crashes into a Manhattan skyscraper if terrorists are *not* attacking Manhattan skyscrapers (i.e., it is an accident): 0.008%

>>>>

Example 3B: Now, consider that a second plane just hit the World Trade Center.
What is the probability that a terror attack occurred given that a second plane hit the World Trade Center?

- the revised [prior probability](#sec-baseRate) that terrorists crash a plane into a Manhattan skyscraper (from [Example 3A](#sec-nateSilverExample3A)): 38.46272%
- the [conditional probability](#sec-conditionalProbability) that a plane crashes into a Manhattan skyscraper if terrorists are attacking Manhattan skyscrapers: 100%
- the [conditional probability](#sec-conditionalProbability) that a plane crashes into a Manhattan skyscraper if terrorists are *not* attacking Manhattan skyscrapers (i.e., it is an accident): 0.008%
